\textcolor{blue}{A gradient-based optimization method for motion planning}$^{1}$

### 2016-01-18 paper.tex
State that we optimize on Riemanian manifolds in a proper way.

>>>>

\textcolor{blue}{Another important feature of our contribution is that we optimize paths on the robot configuration space in a proper mathematical way. Most other optimization algorithms represent $SO3$ rotations by a vector directed along the rotation axis and the norm of which is the rotation angle, also known as the exponential map of $so3$, or even worse by Euler angles.}
